Uppangala tree functionnal: Article draft

### 2016-07-18 inst/doc/draft2.Rmd
v0.1.9019 Rm BIOMASS NAMESPACE & genTrees.R

```{r 6 lm & null models}
reg <- '~ Slope + Curvature + Wetness + SW + Canopy + BA'
LM <- lapply(com, function(x) {with(x@data, list(LES.cwm = lm(formula(paste('LES.cwm', reg))), # CWM
                                                 SLA.cwm = lm(formula(paste('SLA.cwm', reg))), 
                                                 WES.cwm = lm(formula(paste('WES.cwm', reg))),
                                                 WD.cwm = lm(formula(paste('WD.cwm', reg))),
                                                 LDMC.cwm = lm(formula(paste('LDMC.cwm', reg))),
                                                 LA.cwm = lm(formula(paste('LA.cwm', reg))),
                                                 Thick.cwm = lm(formula(paste('Thick.cwm', reg))),
                                                 LES.cwv = lm(formula(paste('LES.cwv', reg))), # CWV
                                                 SLA.cwv = lm(formula(paste('SLA.cwv', reg))), 
                                                 WES.cwv = lm(formula(paste('WES.cwv', reg))),
                                                 WD.cwv = lm(formula(paste('WD.cwv', reg))),
                                                 LDMC.cwv = lm(formula(paste('LDMC.cwv', reg))),
                                                 LA.cwv = lm(formula(paste('LA.cwv', reg))),
                                                 Thick.cwv = lm(formula(paste('Thick.cwv', reg)))))})
LM <- lapply(LM, function(y){lapply(y, function(x){step(x, direction = 'both', trace = 0)})})
Fval <- lapply(LM, function(y){lapply(y, function(x){summary(x)$fstatistic['value']})})
Fval <- lapply(Fval, function(x){do.call('rbind.data.frame', x)})
Fval <- data.frame(Fval)
names(Fval) <- names(LM)

n = 999
nPFT <- rep(list(PFT_sp), n)
nPFT <- lapply(nPFT, function(x){row.names(x) <- sample(row.names(x)) ; return(x)})
nPFT <- lapply(nPFT, function(x){x$Sp_Code <- SpCode[row.names(x)] ; return(x)})
nTrees <- rep(list(Trees[which(names(Trees) %in% c('SpCode', 'com', '2013_girth'))]), n)
nTrees <- lapply(nTrees, function(x){x$ID <- row.names(x) ; return(x)})
nTrees <- mapply(function(x,y){merge(x, y, by.x = 'SpCode', by.y = 'Sp_Code')}, x = nTrees, y = nPFT, SIMPLIFY = F)
nTrees <- lapply(nTrees, function(x){row.names(x) <- x$ID ; return(x)})
nTrees <- lapply(nTrees, function(x){x <- x[-which(names(x) == 'ID')] ; return(x)})
ncom <- lapply(nTrees, function(x){CWT(x, com[[1]])})
ncom <- lapply(ncom, `[`, names(ncom[[1]]))
ncom <- apply(do.call(rbind, ncom), 2, as.list) 
nLM <- rep(list(LM), n)
nLM <- lapply(nLM, `[`, names(nLM[[1]]))
nLM <- apply(do.call(rbind, nLM), 2, as.list)
ncom <- lapply(ncom, function(c){lapply(c, function(x){x <- rep(list(x), 14) ; return(x)})})
nLM <- mapply(function(x,y){
  mapply(function(r,s){
    mapply(function(p,q){
      lm(p$call,q)
    }, p = r, q = s, SIMPLIFY = F)
  }, r = x, s = y, SIMPLIFY = F)
}, x = nLM, y = ncom, SIMPLIFY = F)
nFval <- lapply(nLM, function(lm){lapply(lm, function(y){lapply(y, function(x){summary(x)$fstatistic['value']})})})
nFval <- lapply(nFval, function(x){lapply(x, `[`, names(x[[1]])) ; apply(do.call(rbind, x), 2, as.list)})
nFval <- lapply(nFval, function(f){lapply(f, unlist)})
pval <- 1 - mapply(function(x,y){mapply(function(r,s){rank(c(r,s))[1]/(n+1)}, r = x, s= y)}, x = lapply(as.list(Fval), as.list), y = nFval)
row.names(pval) <- row.names(Fval)
```

>>>>

```{r 6 lm & null models}
reg <- '~ Slope + Curvature + Wetness + SW + Canopy + BA'
LM <- lapply(com, function(x) {with(x@data, list(LES.cwm = lm(formula(paste('LES.cwm', reg))), # CWM
                                                 SLA.cwm = lm(formula(paste('SLA.cwm', reg))), 
                                                 WES.cwm = lm(formula(paste('WES.cwm', reg))),
                                                 WD.cwm = lm(formula(paste('WD.cwm', reg))),
                                                 LDMC.cwm = lm(formula(paste('LDMC.cwm', reg))),
                                                 LA.cwm = lm(formula(paste('LA.cwm', reg))),
                                                 Thick.cwm = lm(formula(paste('Thick.cwm', reg))),
                                                 LES.cwv = lm(formula(paste('LES.cwv', reg))), # CWV
                                                 SLA.cwv = lm(formula(paste('SLA.cwv', reg))), 
                                                 WES.cwv = lm(formula(paste('WES.cwv', reg))),
                                                 WD.cwv = lm(formula(paste('WD.cwv', reg))),
                                                 LDMC.cwv = lm(formula(paste('LDMC.cwv', reg))),
                                                 LA.cwv = lm(formula(paste('LA.cwv', reg))),
                                                 Thick.cwv = lm(formula(paste('Thick.cwv', reg)))))})
LM <- lapply(LM, function(y){lapply(y, function(x){step(x, direction = 'both', trace = 0)})})
# Global F
Fval <- lapply(LM, function(y){lapply(y, function(x){summary(x)$fstatistic['value']})})
Fval <- lapply(Fval, function(x){do.call('rbind.data.frame', x)})
Fval <- data.frame(Fval)
names(Fval) <- names(LM)
# Partial F
# pFval <- lapply(LM, function(y){lapply(y, function(x){car::Anova(x)['F value']})})

n = 999
nPFT <- rep(list(PFT_sp), n)
nPFT <- lapply(nPFT, function(x){row.names(x) <- sample(row.names(x)) ; return(x)})
nPFT <- lapply(nPFT, function(x){x$Sp_Code <- SpCode[row.names(x)] ; return(x)})
nTrees <- rep(list(Trees[which(names(Trees) %in% c('SpCode', 'com', '2013_girth'))]), n)
nTrees <- lapply(nTrees, function(x){x$ID <- row.names(x) ; return(x)})
nTrees <- mapply(function(x,y){merge(x, y, by.x = 'SpCode', by.y = 'Sp_Code')}, x = nTrees, y = nPFT, SIMPLIFY = F)
rm(nPFT)
nTrees <- lapply(nTrees, function(x){row.names(x) <- x$ID ; return(x)})
nTrees <- lapply(nTrees, function(x){x <- x[-which(names(x) == 'ID')] ; return(x)})
ncom <- lapply(nTrees, function(x){CWT(x, com[[1]])})
rm(nTrees)
ncom <- lapply(ncom, `[`, names(ncom[[1]]))
ncom <- apply(do.call(rbind, ncom), 2, as.list) 
nLM <- rep(list(LM), n)
nLM <- lapply(nLM, `[`, names(nLM[[1]]))
nLM <- apply(do.call(rbind, nLM), 2, as.list)
ncom <- lapply(ncom, function(c){lapply(c, function(x){x <- rep(list(x), 14) ; return(x)})})
nLM <- mapply(function(x,y){
  mapply(function(r,s){
    mapply(function(p,q){
      lm(p$call,q)
    }, p = r, q = s, SIMPLIFY = F)
  }, r = x, s = y, SIMPLIFY = F)
}, x = nLM, y = ncom, SIMPLIFY = F)
rm(ncom) ; gc()

# Global model
nFval <- lapply(nLM, function(lm){lapply(lm, function(y){lapply(y, function(x){summary(x)$fstatistic['value']})})})
nFval <- lapply(nFval, function(x){lapply(x, `[`, names(x[[1]])) ; apply(do.call(rbind, x), 2, as.list)})
nFval <- lapply(nFval, function(f){lapply(f, unlist)})

# nDev <- lapply(nLM, function(lm){lapply(lm, function(y){lapply(y, function(x){deviance(x)})})})
# nDev <- lapply(nDev, function(x){lapply(x, `[`, names(x[[1]])) ; apply(do.call(rbind, x), 2, as.list)})
# nDev <- lapply(nDev, function(f){lapply(f, unlist)})
# invisible(mapply(function(x,y,z){plot(x, y, xlab = 'Fval', ylab = 'Dev', main = z)}, x = nFval$abundance, y = nDev$abundance, z = as.list(names(nFval$abundance))))

pval <- 1 - mapply(function(x,y){mapply(function(r,s){rank(c(r,s))[1]/(n+1)}, r = x, s= y)}, x = lapply(as.list(Fval), as.list), y = nFval)
row.names(pval) <- row.names(Fval)

# Partial contribution

```
